
\section{Analysis, discussion, and concluding remarks}
\label{sec:analysis}

\subsection{What makes PDP on (twisted) Edwards curves easier to
  solve?}

As we have seen in Section~\ref{sec:experiment-result}, PDP on
(twisted) Edwards curves seems easier to solve than on other curves.
%
The explanation offered by Faug\`ere, Gaudry, Hout, and Renault is
``due to the smaller degree appearing in the computation of Gr\"obner
basis of $\mathscr S_{D_n}$ in comparison with the Weierstrass case,''
cf.~Section~4.1.1 of their
paper~\cite{DBLP:journals/joc/FaugereGHR14}.
%
Unfortunately, this \emph{cannot} explain the difference between
(twisted) Edwards and Montgomery curves, as the highest degrees
appearing in the computation of Gr\"obner bases are \emph{the same}
for these two curves.
%
Therefore, there must be other reasons.
%
Table~\ref{tb:terms} shows the sparsity of the polynomials before and
after Weil restriction for each of the four curves under investigation
in the case of $m=2,3,4$.
%
As there are $n$ polynomials after Weil restriction, we only show the
average numbers here.
%
We also include the maximum number of terms for a polynomial of degree
$2^{(m+1)-2}$ in $m$ variables.
%
\input{result2}

We can see that total number of terms for twisted Edwards curves is
significantly fewer than that for the other curves in all cases.
%
Naturally, this could lead to faster solving time with the F4
algorithm.
%
We also note that, except for twisted Edwards curves, the summation
polynomials before Weil restriction for the other curves are all 100\%
dense without any missing terms.

% We further analyze which terms are missing from the summation
% polynomials for curves in different forms.
% %
% We classify terms into odd vs.~even degrees.
% %
% From Table~\ref{tb:terms}, missing of only odd terms on twisted Edwards
% curve reduce the number of terms.

\input{tEdwards}


\subsection{What price for a highly symmetric factor base?}
\label{sec:price}

Last but not least, we discuss the price needed to pay to have a
highly symmetric factor base $\mathcal F$ that is invariant under more
group actions in addition to that of the symmetric group $S_m$.
%
As previewed in Section~\ref{sec:symmetry-decomposition-probability},
we would expect that the effect of the decrease in decomposition
probability due to additional symmetry in $\mathcal F$ could be offset
by that of the increase in number of solutions.
%
For example, let us reconsider the group action of addition of $T_2$
in Section~\ref{sec:exploit-symmetry}.
%
If we could get $2^{m-1}$ solutions, then the loss of the factor of
$2^{m-1}$ in decomposition probability would be compensated.
%
This way everything would be the same as if there were no such
symmetry, and we could exploit the additional symmetry at no cost.

Unfortunately, this proposition is \emph{false} in general.
%
Consider an example of $m=4$.
%
Let $Q_i=P_i+ T_2$ for $i=1,2,3,4$.
%
We can write down all $2^{m-1}=8$ possible ways of a point
decomposition under this group action:
%
\[ \begin{aligned}
P_1 + P_2 + P_3 + P_4 = & Q_1 + Q_2 + P_3 + P_4 \\
= Q_1 + P_2 + Q_3 + P_4 = & Q_1 + P_2 + P_3 + Q_4 \\
= P_1 + Q_2 + Q_3 + P_4 = & P_1 + Q_2 + P_3 + Q_4 \\
= P_1 + P_2 + Q_3 + Q_4 = & Q_1 + Q_2 + Q_3 + Q_4.
\end{aligned} \]
%
It is easy to find that we have only 5 linearly independent relations
from these 8 relations, as there are nontrivial linear combinations
summing to zero, e.g.:
\[ (P_1 + P_2 + P_3 + P_4) - (Q_1 + Q_2 + P_3 + P_4) - (P_1 + P_2 +
  Q_3 + Q_4) + (Q_1 + Q_2 + Q_3 + Q_4) = \mathcal O.\]


As explained in Section~\ref{subsec:conditions}, the factor bases for
Montgomery and twisted Edwards curves are invariant under addition of
2-torsion points.
%
For $m=3$, we achieve maximum rank of $2^{m-1}=4$.
%
For $m=4$, as we have explained above, we can only have rank $5$, 
which is strictly less than the maximum possible rank $2^{m-1}=8$.

Finally, we note that we have not exploited any symmetry for Hessian
curves in our experiments.
%
However, the rank for Hessian curves is always 1 in all our
experiments.
%
This shows that the factor base we have chosen for Hessian curves is
\emph{not} invariant under addition of small torsion points, as the
rank would be $>1$ otherwise.





