%
%
% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{algpseudocode,amsfonts,amsmath,amssymb}
%\usepackage[scale=.8]{geometry}
% \geometry{
%   a4paper,         % or letterpaper
%   textwidth=15cm,  % llncs has 12.2cm
%   textheight=24cm, % llncs has 19.3cm
%   heightrounded,   % integer number of lines
%   hratio=1:1,      % horizontally centered
%   vratio=2:3,      % not vertically centered
% }
\usepackage{latexsym,mathrsfs,multirow}
%
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\res}{Res}
\DeclareMathOperator{\sgn}{sgn}
\newcommand{\F}[1]{\ensuremath{\mathbb F_{#1}}}
%\def\F{{\mathbb F}}
\def\Fqn{{\mathbb F}_{p^n}}
\def\Fqm{{\mathbb F}_{p^m}}
\def\qed{\hfill $\Box$}
\long\def\comment#1{}
%
\begin{document}
%
\title{On the computational complexity of ECDLP for elliptic curves in
  various forms using index calculus}
%
%\titlerunning{}
%
\author{Chen-Mou~Cheng \and Kenta~Kodera \and Atsuko~Miyaji}
%
\authorrunning{Cheng, Kodera, and Miyaji}
%
%\institute{Osaka University, Japan}
\institute{Graduate School of Engineering, Osaka University \\
\email{\{ccheng, kodera\}@cy2sec.comm.eng.osaka-u.ac.jp,
miyaji@comm.eng.osaka-u.ac.jp}
}           %  \\
%\institute{Graduate School of Engineering, Osaka University, 2-1 Yamadaoka Suita Osaka, Japan,. \\
%              Tel.: +81-6-6879-7714 \\
%              Fax: +81-6-6879-7714 \\
% \email{miyaji@comm.eng.osaka-u.ac.jp}           %  \\

\maketitle              % typeset the title of the contribution

\begin{abstract}
%
  The security of elliptic curve cryptography is closely related to
  the computational complexity of the elliptic curve discrete
  logarithm problem (ECDLP).
%
  Today, the best practical attacks against ECDLP are
  exponential-time, generic discrete logarithm algorithms such as
  Pollard's rho method.
%
  Recently, there is a line of research on index calculus for ECDLP
  started by Semaev, Gaudry, and
  Diem.
%
  Under certain heuristic assumptions, such algorithms could lead to
  subexponential attacks to ECDLP in some
  cases.
%
  In this paper, we investigate the computational complexity of ECDLP
  for elliptic curves in various forms---including
  Hessian,
  Montgomery, (twisted)
  Edwards,
  and Weierstrass using index calculus.
%
  The research question we would like to answer is: Using index
  calculus, is there any significant difference in the computational
  complexity of ECDLP for elliptic curves in various forms?
%
  We will provide some empirical evidence and insights showing an
  affirmative answer in this paper.
%
  \keywords{Security evaluation, ECDLP, index calculus, summation
    polynomial, point decomposition problem}
\end{abstract}

\input{introduction}
\input{index-calculus}
\section{Montgomery and Hessian curves}
\label{sec:montgomery-hessian}
\input{montgomery}
\input{hessian}
\input{experiment}
\input{analysis}
\input{conclusion}

\section*{Acknowledgments}
%
This work is partially supported by JSPS KAKENHI Grant (C)(JP15K00183)
and (JP15K00189) and Japan Science and Technology Agency, CREST and
Infrastructure Development for Promoting International S\&T
Cooperation and Project for Establishing a Nationwide Practical
Education Network for IT Human Resources Development, Education
Network for Practical Information Technologies.
%

%
% ---- Bibliography ----
%
\bibliographystyle{abbrv}
\bibliography{dblp,local}

\end{document}
