%
% Experimental results
%

\section{Experimental results and concluding remarks}\label{sec:experimental-results}
%
\subsection{Security consideration of ECDLP over OEF}
%
An OEF $\Fqn$ is typically used to achieve highly efficient software
implementation.
%
From the security point of view, $n$ is recommended to be a prime
since $E(\Fqm) \subset E(\Fqn)$ yields $\#E(\Fqm) \mid \# E(\Fqn)$ for
$m \mid n$.
%
However, we have not seen relation between parameters $(p, n)$ of OEF,
and the security of ECDLP over an OEF $\Fqn$.
%
For example, suppose that we use OEFs of $\F{{p_{32}}^5}$,
$\F{{p_{16}}^{11}}$, and $\F{{p_{8}}^{19}}$, where $p_{32}, p_{16}$,
and $p_{8}$ are primes close to $2^8, 2^{16}$, and $2^{32}$,
respectively.
%
These OEFs satisfy a condition of prime extension degree of 5, 11, and
19, respectively, and have almost the same number of rational points,
$\#E(\F{{p_{32}}^5}) \sim \#E(\F{{p_{16}}^{11}}) \sim
\#E(\F{{p_{8}}^{19}})$.
%
Now we pose a question: Using index calculus algorithm described in
Section~\ref{subsec:TSPL}, is there any significant difference in the
computational complexity of solving ECDLP for $\F{{p_{32}}^5}$,
$\F{{p_{16}}^{11}}$, and $\F{{p_{8}}^{19}}$?
%
We will provide some empirical evidence showing an affirmative answer
in the next section.

\subsection{Experiment 1: Exploiting the symmetry}
%
We conducted two experiments using (single-threaded) MAGMA on Intel
Xeon CPU E7-4830 v4 running at 2~GHz.
%
First, we show that using symmetry on Montgomery curves can
significantly speed up relation collection in index calculus.
%
Specifically, we choose $\F{2^{16} - 165}$, over which we generate
several random Weierstrass and Montgomery curves.
%
We then try to decompose several random points into $m$ points from a
factor base consisting of points whose $x$-coordinates are in \F p.
%
The results of the first experiment are summarized in
Table~\ref{tab:exp-sym}.
%
\begin{table}
  \begin{center}
    \begin{tabular}{|r||r|r|r|r|r|r|}
      \hline
      & \multicolumn{2}{c|}{Weierstrass} & \multicolumn{2}{c|}{Montgomery (plain)} & \multicolumn{2}{c|}{Montgomery (sym.)} \\ \hline\hline
      m & Dreg     & Matcost      & Dreg     & Matcost      & Dreg     & Matcost      \\ \hline
      2 & 2        & 2406.6      & 3        & 3206.7      & 2        & 2406.6      \\ \hline
      3 & 6        & 3466021.3    & 6        & 4344579.2    & 6        & 3465410.9    \\ \hline
    \end{tabular}
  \end{center}
  \caption{Experimental results for symmetry exploiting on Montgomery curves.}
  \label{tab:exp-sym}
\end{table}
%
In Table~\ref{tab:exp-sym}, we report the degree of regularity (Dreg)
and the matrix cost in MAGMA's F4 algorithm (Matcost).
%
As we can see, without using the symmetry, it generally takes longer
time to decompose over Montgomery curves, whereas it roughly takes the
same amount of time for Weierstrass curves and Montgomery curves after
taking symmetry into account.

\subsection{Experiment 2: Security evaluation for various OEFs}
%
In this experiment, we would like to evaluate the security of
Montgomery curves over various OEFs; the results are summarized in
Table~\ref{tab:experimental-results}.
%
All timing results are reported in seconds unless otherwise specified.
%
We choose several OEFs suggested by Bailey and
Paar~\cite{DBLP:conf/crypto/BaileyP98}, over which we study the
complexity of the relation collection phase of the index calculus
algorithm for solving ECDLP on several random Montgomery curves.
%
Specifically, for each curve $E$ we first choose a random rational
point $P$ whose order is prime and close to the size of the underlying
OEF \F{p^n}.
%
We then decide a factor base $\mathcal F$ using a vector subspace $V$
of \F{p^n} over \F p, i.e., $|\mathcal F|\approx p^{\dim V}$, which,
together with the linear algebra constant, determines the linear
algebra time (``T\textsubscript L'' in
Table~\ref{tab:experimental-results}).
%
The bulk of our experimentation then involves generating random points
in $\langle P\rangle$ \emph{known} to be decomposable into a sum of
$m$ points from $\mathcal F$.
%
As noted by Galbraith and Gebregiyorgis, the time for solving such
instances tends to be larger than that for attempting to decompose
points that \emph{cannot} be decomposed
so~\cite{DBLP:conf/indocrypt/GalbraithG14}.
%
In general, the success probability of such point decomposition is
roughly $\mathcal O(p^{m\dim V - n}/m!)$ for $m\dim V<n$, which is
taken into account in estimating the relation collection time
(``T\textsubscript R'' in Table~\ref{tab:experimental-results}).
%
\begin{table}
  \begin{center}
    \begin{tabular}{llcr}
      OEF & $\ord(P)$ & $\dim V$ & T\textsubscript R$+$T\textsubscript L \\ \hline
      \F{241^{19}} & $\mathcal O(2^{147})$ & 5 & $212.4\times\mathcal O(2^{72})+\mathcal O(2^{80})$ \\
      \F{65371^{11}} & $\mathcal O(2^{173})$ & 4 & $37.6\times\mathcal O(2^{49})+\mathcal O(2^{129})$ \\
      \F{4294967291^5} & $\mathcal O(2^{154})$ & 2 & $0.04\times\mathcal O(2^{65})+\mathcal O(2^{129})$
    \end{tabular}
  \end{center}
  \caption{Security evaluation of Montgomery curves of various OEFs for $m=2$.}
  \label{tab:experimental-results}
\end{table}
%
It is interesting to note that the complexity for the relation
collection phase is quite different for different OEFs, even though we
use the same Weil descent algorithm.
%
However, as we can see from Table~\ref{tab:experimental-results}, such
index calculus algorithm cannot yet outperform the generic algorithms
such as Pollard's rho method, as the linear algebra phase takes
significantly longer time.

% \section{Concluding remarks}
% %
% \label{sec:conclusions}
%
